Combinatorial Identities from Lagrange's Interpolation Polynomial

### 2020-12-09 spectral radius of matrix new method/thesis/article120920.tex
120920 whole article

 找到一個簡單而且傑出的方法來估算譜半徑，試著縮小誤差，必定存在一個方法理性地證明它。我知道譜半徑是區分
 圖中點連線關係的重要指標，所以找一個簡單的方法來估算譜半徑是很有意義的。有了穩固的證明，我們可以估計連
 接矩陣的最小誤差譜半徑，並且找出存在這樣的上下界的充分條件。\\
\bigskip

@@

%\begin{abstract}
\addcontentsline{toc}{section}{Abstract (in English)}
Find a simple and excellent executable method
 to estimate spectral radius, try to minimize the bios and there is a way to prove it sensible.
 I know that spectral radius is an important index to specify the relation of connected vertices in
  the graphs, so it is meanful to find a simple method to estimate spectral readius. With a solid proof,
   we can estimate the spectral radius of an adjacent matrix with minimal error and find out the sufficent
  condition on the existence of such bound.

@@

\begin{defn}       
Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a
 nonzero column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ 
of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$

%Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
\end{defn}

@@

\begin{defn}
Given an undirected graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
 radius of the adjacency matrix of G.
\end{defn}

>>>>

 我知道譜半徑是區分圖中點連線關係的重要指標，所以找一個簡單的方法來估算譜半徑
 是很有意義的。一個簡單而且傑出估算譜半徑的方法有一些特徵。首先，誤差被極小化
 ，第二必定存在一個方法正確理性地證明它。列舉這些方法並正確證明會讓這方法穩固
 且可信靠。在估計的領域裡，最好思考過所有的因素，再根據目標，取用估計譜半徑的
 方法，以利之後分析圖的連接矩陣，與其連通性有關的矩陣。
 \\
\bigskip

@@

%\begin{abstract}
\addcontentsline{toc}{section}{Abstract (in English)}
I know that spectral radius is an important index to specify the relation of connected vertices in
 the graphs, so it is meanful to find a simple method to estimate spectral readius. A simple and excellent
 executable method to estimate spectral radius has some features. First, the bios is minimized, and second
 there must be a way to prove it sensible. Enumerate these factors and prove it correctly would make this method
 solid and reliable. In the field of estimation, it's better to go through all the factors, and base on one's goal
 to apply the methods of estimating spectral radius before analyzing the adjacency matrix of the graphs, which is
 related to the connectness of the graph.

@@

\begin{defn}       
Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a
 nonzero column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$ 
of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$
%Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
\end{defn}

@@

\begin{defn}
    Given a directed graph G, the $\textit{spectral radius}$  $\rho(G) $ of G is the spectral
     radius of the adjacency matrix of G.
\end{defn}
